---
title: "Stream Temperature Graphs"
author: "Michael Hayden"
date: "7/7/2017"
output: html_document
---

### Load Packages
```{r setup , message=FALSE , echo= FALSE , warning=FALSE}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(lubridate))
```

### Load Data
```{r , message=FALSE , echo= FALSE , warning=FALSE}
setwd('/Users/michaeljames/Documents/MastersProject/FishSampling/FishSampling_R/DataIn/Temperature/ProcessedTempData')
#masterTemp <- read.csv("masterTemp.csv" , header = TRUE) 
tempData <- read.csv("tempData.csv" , header = TRUE) %>%
            filter(year %in% (2015:2017) , site %in% c("Below Webber Road" , "Lower")) %>%
            mutate(
              detectionDate = ymd(detectionDate))
```

### Mean Temperature

#### Daily Mean Temperature By River and Year
```{r , message=FALSE , echo= FALSE , warning=FALSE}
tempData %>% filter(year %in% (2015:2017) , site %in% c("Below Webber Road" , "Lower")) %>%
             ggplot(aes(y = meanTemp , x = dayOfYear , colour = river)) +
              geom_point() +
              labs(x = "Day Of the Year" , y = "Mean Temperature (Degrees C)" , col = "River") +
              facet_grid(river~year)
```

#### Violin Daily Mean Temperature By River and Year
```{r , message=FALSE , echo= FALSE , warning=FALSE}
tempData %>% ggplot(aes(y = meanTemp , x = as.factor(month) , fill = as.factor(river))) +
               geom_violin() +
               labs(x = "Day Of the Year" , y = "Mean Temperature (Degrees C)" , fill = "River")+
               facet_grid(river~year)
```

#### Spring Daily Mean Temperature By Year
```{r , message=FALSE , echo= FALSE , warning=FALSE}
tempData %>% filter(year %in% (2015:2017) , dayOfYear < 200) %>%
             ggplot(aes(y = meanTemp , x = dayOfYear , colour = river)) +
              geom_point() +
              labs(x = "Day Of the Year" , y = "Mean Temperature (Degrees C)" , col = "River") +
              facet_wrap(~year)
```

#### Spring Daily Mean Temperature By River
```{r , message=FALSE , echo= FALSE , warning=FALSE}
tempData %>% filter(dayOfYear %in% 50:200) %>% 
             ggplot(aes( x = dayOfYear , y = meanTemp , colour = as.factor(year))) +
               geom_line() +
               labs(x = "Day Of the Year" , y = "Mean Temperature " , col = "River") +
               facet_wrap(~river)
```

#### Spring Daily Mean Temperature By Year
```{r , message=FALSE , echo= FALSE , warning=FALSE}
tempData %>% filter(dayOfYear %in% 50:200) %>% 
             ggplot(aes( x = dayOfYear , y = meanTemp , colour = as.factor(river))) +
               geom_line() +
               labs(x = "Day Of the Year" , y = "Mean Temperature " , col = "River") +
               facet_wrap(~year)
```

#### Spring Temperature Data by River and Year Violin
```{r , message=FALSE , echo= FALSE , warning=FALSE}
tempData %>%  filter(dayOfYear %in% (0:200)) %>%
              ggplot( aes( y = meanTemp , x = as.factor(month ))) + 
                geom_violin() +
                labs(x = "Day Of the Year" , y = "Mean Temperature (Degrees C)" , col = "River") +
                facet_grid(year~river)
```

### Cumulitive Degree Days

#### Degree Days Facet By Year
```{r , message=FALSE , echo= FALSE , warning=FALSE}
tempData %>% filter(samplingYear %in% 2017 , dayOfYear < 150 , river %in% c("Sanderson" , "Sanderson Upper" , "Sanderson Middle"))%>%
             ggplot(aes(y= degreeDay , x = dayOfYear , colour = as.factor(river))) +
              geom_point(size = 0.5) + 
              labs(x = "Day Of the Year" , y = "Cumulative Degree Days" , col = "River") 
```

#### Degree Days Facet by Stream
```{r , message=FALSE , echo= FALSE , warning=FALSE}
tempData %>% filter(samplingYear %in% 2015:2017 , dayOfYear < 170) %>%
               ggplot(aes(x = dayOfYear , y = degreeDay , colour = as.factor(year))) +
                geom_point(size = 0.5) +
                labs(x = "Day Of the Year" , y = "Cumulative Degree Days" , col = "River") +
                facet_wrap(~river)
```

#### Cumulitive Degree Days Years
```{r , message=FALSE , echo= FALSE , warning=FALSE}
tempData %>% filter(samplingYear %in% 2015:2017) %>%
              ggplot(aes(x = detectionDate , y = degreeDay , colour = as.factor(river))) + 
               geom_point() + 
               labs(x = "Day Of the Year" , y = "Cumulative Degree Days" , col = "River") +
               scale_x_date(date_breaks = "3 month" , date_labels = "%Y-%m" ) +
               theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```

